### 2025-05-25 ms.qmd
Update ms.qmd

## Results
```{r, models_mass}
#| label: models
#| echo: false
#| warning: false

# Delta mass L. delicata
  deli_mod <- brm(rescaled_delta_mass ~ food_ingested+cort*temp, data = deli_stressor_2, family = gaussian(link = "identity"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  plot(deli_mod)
  summary(deli_mod)
# Delta mass L. guichenoti
  guich_mod <- brm(rescaled_delta_mass ~ food_ingested+cort*temp, data = guich_stressor_2, family = gaussian(link = "identity"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(guich_mod)
bayes_R2(guich_mod)

      # Seems that only food ingestion is significant in both species

# Frozen behaviour L. delicata
  deli_mod <- brm(log(lat_to_move+1) ~ Day*cort*temp + (1|lizard), data = deli_stressor, family = gaussian(link = "identity"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(deli_mod)
  plot(deli_mod)
bayes_R2(deli_mod)

# Frozen behaviour L. delicata
 guich_mod <- brm(log(lat_to_move+1) ~ Day*cort*temp + (1|lizard), data = guich_stressor, family = gaussian(link = "identity"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(guich_mod)
  plot(guich_mod)
bayes_R2(guich_mod)

# Extract posteriors
posterior <- posterior_samples(mod, pars = "^b")
plyr::ldply(lapply(posterior, mean))
plyr::ldply(lapply(posterior, function(x) quantile(x, c(0.025, 0.975))))
temp23 <- c(posterior[,"b_Intercept"], (posterior[,"b_Intercept"]+ posterior[,"b_trtB_23"]))
temp28 <- c((posterior[,"b_Intercept"] + posterior[,"b_trtB_28"]), posterior[,"b_trtB_23"])

pmcmc(temp23 - temp28)
dharma(GMM_deli2)

>>>>

## Results
```{r, models_mass}
#| label: models_mass
#
# A) L. delicata
deli_mod_mass <- brm(rescaled_delta_mass ~ food_ingested+cort*temp, data = deli_stressor_2, family = gaussian(link = "identity"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  plot(deli_mod)
  summary(deli_mod)
# Delta mass L. guichenoti
  guich_mod <- brm(rescaled_delta_mass ~ food_ingested+cort*temp, data = guich_stressor_2, family = gaussian(link = "identity"), chains = 4, cores = 4, iter = 2000, warmup = 1000, control = list(adapt_delta = 0.99))
  summary(guich_mod)
bayes_R2(guich_mod)
```
